\pkg{cv}: An \proglang{R} Package for Cross-Validation of Regression Models

### 2024-01-12 scratch/notes_john/JSS-article/JSS-article-reduced.Rmd
fix typo in JSS paper

* \code{method}, the computational method to employ: \code{"hatvalues"} is relevant only for LOO CV and bases computation on the hatvalues for the linear model; \code{"Woodbury"} employs the Woodbury matrix to compute the CV criterion with each fold deleted; \code{"naive"} updates the model using the \code{update()} function; and \code{"auto"} selects \code{"hatvalues"} for LOO CV and \code{"Woodbury"} for $k$-fold CV, both of which are much more efficient than literally updating the least-squares fit (see below and Section \ref{efficient-computation-for-linear-and-generalized-linear-models}).

>>>>

* \code{method}, the computational method to employ: \code{"hatvalues"} is relevant only for LOO CV and bases computation on the hatvalues for the linear model; \code{"Woodbury"} employs the Woodbury matrix to compute the CV criterion with each fold deleted; \code{"naive"} updates the model using the \code{update()} function; and \code{"auto"} selects \code{"hatvalues"} for LOO CV and \code{"Woodbury"} for $k$-fold CV, both of which are much more efficient than literally updating the least-squares fit (see below and Section \ref{efficient-computations-for-linear-and-generalized-linear-models}).

### 2024-01-12 scratch/notes_john/JSS-article/JSS-article-reduced.tex
fix typo in JSS paper

\begin{itemize}
\item
  \code{model}, an \code{"lm"} object, the only required argument.
\item
  \code{data}, which can usually be inferred from the \code{model}
  object.
\item
  \code{criterion}, a function to compute the CV criterion (defaulting
  to \code{mse}).
\item
  \code{k}, the number of folds to employ (defaulting to \code{10}); the
  character value \code{"n"} or \code{"loo"} may be supplied to specify
  leave-one-out cross-validation.
\item
  \code{reps}, the number of times to repeat the CV procedure
  (defaulting to 1).
\item
  \code{seed}, the seed for \proglang{R}'s pseudo-random number
  generator; if not specified a value is randomly selected, reported,
  and saved, so that the CV procedure is replicable.
\item
  \code{confint}, whether or not to compute a confidence interval for
  the CV criterion, defaulting to \code{TRUE} if there are at least 400
  cases; a confidence interval is computed only if the CV criterion can
  be expressed as the average of casewise components (see Section
  \ref{computation-of-the-bias-corrected-cv-criterion-and-confidence-intervals}
  for details).
\item
  \code{level}, the level for the confidence interval (defaulting to
  \code{0.95}).
\item
  \code{method}, the computational method to employ: \code{"hatvalues"}
  is relevant only for LOO CV and bases computation on the hatvalues for
  the linear model; \code{"Woodbury"} employs the Woodbury matrix to
  compute the CV criterion with each fold deleted; \code{"naive"}
  updates the model using the \code{update()} function; and
  \code{"auto"} selects \code{"hatvalues"} for LOO CV and
  \code{"Woodbury"} for \(k\)-fold CV, both of which are much more
  efficient than literally updating the least-squares fit (see below and
  Section
  \ref{efficient-computation-for-linear-and-generalized-linear-models}).
\item
  \code{ncores}, the number of cores to employ for parallel computation;
  if \code{cores = 1} (the default), the computations are not
  parallelized.
\end{itemize}

@@

Residual standard error: 4.374 on 389 degrees of freedom
Multiple R-squared:  0.6876,    Adjusted R-squared:  0.686 
F-statistic:   428 on 2 and 389 DF,  p-value: < 2.2e-16
\end{CodeOutput}
\begin{CodeInput}
R> cv(m.auto, confint=TRUE)
\end{CodeInput}
\begin{CodeOutput}
R RNG seed set to 32925
\end{CodeOutput}
\begin{CodeOutput}
10-Fold Cross Validation
method: Woodbury
criterion: mse
cross-validation criterion = 19.41501
bias-adjusted cross-validation criterion = 19.3924
95% CI for bias-adjusted CV criterion = (15.88674, 22.89806)
full-sample criterion = 18.98477 
\end{CodeOutput}
\end{CodeChunk}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> BayesRule
\end{CodeInput}
\begin{CodeOutput}
function(y, yhat){
  if (!all(y %in% c(0, 1))) stop("response values not all 0 or 1")
  if (any(yhat < 0) || any(yhat > 1)) stop("fitted values outside of interval [0, 1]")
  yhat <- round(yhat)
  result <- mean(y != yhat) # proportion in error
  attr(result, "casewise loss") <- "y != round(yhat)"
  result
}
<bytecode: 0x13e7ed098>
<environment: namespace:cv>
\end{CodeOutput}
\end{CodeChunk}

>>>>

\begin{itemize}
\item
  \code{model}, an \code{"lm"} object, the only required argument.
\item
  \code{data}, which can usually be inferred from the \code{model}
  object.
\item
  \code{criterion}, a function to compute the CV criterion (defaulting
  to \code{mse}).
\item
  \code{k}, the number of folds to employ (defaulting to \code{10}); the
  character value \code{"n"} or \code{"loo"} may be supplied to specify
  leave-one-out cross-validation.
\item
  \code{reps}, the number of times to repeat the CV procedure
  (defaulting to 1).
\item
  \code{seed}, the seed for \proglang{R}'s pseudo-random number
  generator; if not specified a value is randomly selected, reported,
  and saved, so that the CV procedure is replicable.
\item
  \code{confint}, whether or not to compute a confidence interval for
  the CV criterion, defaulting to \code{TRUE} if there are at least 400
  cases; a confidence interval is computed only if the CV criterion can
  be expressed as the average of casewise components (see Section
  \ref{computation-of-the-bias-corrected-cv-criterion-and-confidence-intervals}
  for details).
\item
  \code{level}, the level for the confidence interval (defaulting to
  \code{0.95}).
\item
  \code{method}, the computational method to employ: \code{"hatvalues"}
  is relevant only for LOO CV and bases computation on the hatvalues for
  the linear model; \code{"Woodbury"} employs the Woodbury matrix to
  compute the CV criterion with each fold deleted; \code{"naive"}
  updates the model using the \code{update()} function; and
  \code{"auto"} selects \code{"hatvalues"} for LOO CV and
  \code{"Woodbury"} for \(k\)-fold CV, both of which are much more
  efficient than literally updating the least-squares fit (see below and
  Section
  \ref{efficient-computations-for-linear-and-generalized-linear-models}).
\item
  \code{ncores}, the number of cores to employ for parallel computation;
  if \code{cores = 1} (the default), the computations are not
  parallelized.
\end{itemize}

@@

Residual standard error: 4.374 on 389 degrees of freedom
Multiple R-squared:  0.6876,    Adjusted R-squared:  0.686 
F-statistic:   428 on 2 and 389 DF,  p-value: < 2.2e-16
\end{CodeOutput}
\begin{CodeInput}
R> cv(m.auto, confint=TRUE)
\end{CodeInput}
\begin{CodeOutput}
R RNG seed set to 735559
\end{CodeOutput}
\begin{CodeOutput}
10-Fold Cross Validation
method: Woodbury
criterion: mse
cross-validation criterion = 19.44017
bias-adjusted cross-validation criterion = 19.41622
95% CI for bias-adjusted CV criterion = (15.87764, 22.95479)
full-sample criterion = 18.98477 
\end{CodeOutput}
\end{CodeChunk}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> BayesRule
\end{CodeInput}
\begin{CodeOutput}
function(y, yhat){
  if (!all(y %in% c(0, 1))) stop("response values not all 0 or 1")
  if (any(yhat < 0) || any(yhat > 1)) stop("fitted values outside of interval [0, 1]")
  yhat <- round(yhat)
  result <- mean(y != yhat) # proportion in error
  attr(result, "casewise loss") <- "y != round(yhat)"
  result
}
<bytecode: 0x13db9d388>
<environment: namespace:cv>
\end{CodeOutput}
\end{CodeChunk}
